%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%-------------------------------------------------------------------------------
\cventry
{Travizory Border Security SA.} % Organization
{Machine Learning Engineer (Python/C++)} % Job title
{Neuchatel, Switzerland} % Location
{2022 - 2024} % Date(s)
{
  \begin{cvitems} % Description
    \item {
    Architected a real-time video inference platform running on 
    bare-metal Kubernetes as part of an edge-to-cloud Digital Identity Management 
    System. The microservices archicture used a high speed ZeroMQ based event bus for data 
    throughput. FastAPI provided management REST endpoints, and WebSockets to 
    serve a stream of biometric events to frontend clients.}
    \item {
    Offline data management and data processing workflows runing on kubernetes with 
    scalable distributed task queues to synchronize data in AWS S3 
    to on-premises MinIO object stores and MariaDB using Celery tasks and Redis. 
    The workflows consumed biometric image objects, extracted and store 
    face embeddings and built vector indexes used for online vector similarity search.}
    \item {
    Developed pipelines for real-time video acquisition from GigE Vision industrial cameras 
    ingesting directly into bare-metal Kubernetes clusters using macvlan networking and Multus CNI. 
    The video streams were used for biometric face detection at airport borders achieving 
    100 ms face recognition latency at 30 FPS.}
  \end{cvitems}
}

%-------------------------------------------------------------------------------
\cventry
  {AxonVIBE AG.} % Organization
  {Data Scientist (Java/Python)} % Job title
  {Luzern, Switzerland} % Location
  {2018 - 2021} % Date(s)
  {
    \begin{cvitems} % Description
      \item {
          Developed cloud based real-time serverless time-series data ingestion 
          from mobile device sensors (GPS/IMU) using AWS Lambda and Batch. These 
          provided sliding window feature extraction, data-monitoring, and anomaly 
          detection for building ML models and used Apache Beam and Tensorflow TFX.}
      \item {
          Developed data models and unsupervised learning for a set of Spring Boot 
          microservices that perform hierarchical spatiotemporal clustering for 
          Significant Location and user trajectory detection for a location based 
          contextual platform infering users travel behavioral patterns}
      \item {
          Developed pipelines for hyper-parameter search, model training and model 
          evaluating for Neural Networks, Random Forests and Gradient Boosting Machines.}
    \end{cvitems}
  }

%-------------------------------------------------------------------------------
\cventry
{bbv Software Services AG.} % Organization
{Senior Software Engineer (C++/Java)} % Job title
{Luzern, Switzerland} % Location
{2010 - 2018} % Date(s)
{
  \begin{cvitems} % Description
    \item {
        Consultant Engineer involved in Agile projects for multinational
        customers. Used Scrum and Kanban to iteratively deliver 
        value. Integrated constantly, refactored ruthlessly, and avoided smells. 
        Favoured SOLID principles. Relied on design patterns to produce clean, 
        testable code measured using static analysis.
        }
    \item {
      Developed in modern C++ for embedded Linux and RTOS targets under
      multiple architectures (ARM/PowerPC) and with cross-toolchains. Included 
      Fieldbus based realtime distributed controls for industrial robotics, 
      interfacing with Java Card algorithms running on tamper-resistant smartcards 
      for security modules (SSL/TLS) embedded in Industrial IoT Gateways.}
    \item {
      Developed a system to automated Quality Assurance for medical mobile apps
      running on multiple device models (Android, iOS) using Java, Cucumber specifications, Jenkins CI and Appium. 
      }  
  \end{cvitems}
}

%-------------------------------------------------------------------------------
\cventry
{Hagenbuch Hydraulic Systems AG.} % Organization
{Software Engineer (C++)} % Job title
{Luzern, Switzerland} % Location
{2006 - 2010} % Date(s)
{
  \begin{cvitems} % Description
    \item {
      Development of real-time motion controls for 6-DOF parallel 
      kinematic manipulators (Hexapods) using Fieldbus distributed controllers 
      and input signals from positional encoders and force sensors.}
    \item {
      Online signal processing and analytics in the time and frequency domains for 
      vibration analytics systems. Spectral analysis, and development of 
      real-time data visualization applications.}
  \end{cvitems}
}

%-------------------------------------------------------------------------------
\cventry
{European Organization for Nuclear Research (CERN)} % Organization
{Physics Research Fellow (Beamlines)} % Job title
{Geneva, Switzerland} % Location
{2003 - 2006} % Date(s)
{
  \begin{cvitems} % Description
    \item {
      Monte-Carlo simulation of intranuclear cascades, multi-particle 
      transport to predict radiation induced Single Event Errors (SSE) and 
      Total Ionizing Dose (TID) in LHC control electronics under 
      beam accident scenarios and ensure correct LHC operation.}
      \item {
        Execution of long time-frame scientific workloads on the CERN HPC 
        batch compute system.
        }  
      \item{
      Scientific data analysis and visualization in Matlab prior to presentation 
      of findings to the LHC collaboration and international scientific conferences
      to inform the LHC accelerator design effort.}
  \end{cvitems}
}

%-------------------------------------------------------------------------------
\cventry
{H. H. Wills Physics Laboratory, University of Bristol} % Organization
{Post Doctoral Research Associate (Particle Physics)} % Job Title
{Geneva, Switzerland} % Location
{2001 - 2003} % Date(s)
{
  \begin{cvitems} % Description
    \item {
      Member of the LHCb collaboration searching for the source of matter-antimatter 
      asymmetry in the universe.} 
    \item {
      Prototyping of a Hybrid Photon Detector (HPD) based Ring Imaging Cherenkov 
      Detector (RICH) that provides particle Identity (PID) for physics event 
      reconstruction following LHC proton-proton collisions.}
    \item {
      Developed simulations of HPD response signals and RICH physics event 
      reconstruction software for the LHCb Data Processing Framework and helped 
      define the Physics Data Model. Performed Scientific Data Analysis using 
      ROOT Data Analysis Framework.
        }
  \end{cvitems}
}

%-------------------------------------------------------------------------------
\cventry
{H. H. Wills Physics Laboratory, University of Bristol} % Organization
{Doctoral Researcher (Particle Physics)} % Job Title
{Bristol, UK} % Location
{1998 - 2001} % Date(s)
{
  \begin{cvitems} % Description
    \item {
      Member of the CMS collaboration focussed on the search for the Higgs at the LHC.}
    \item {
      Prototyping of an Avalanche Photodiode (APD) and Vacuum Phototriode (VPT) 
      based Electromagnetic Calorimetor (ECAL) used to measure the energy 
      of photons and electrons in sub-atomic particles cascades produced by 
      LHC proton-proton collisions.}
    \item {
      Development of event reconstruction algorithms for relativistic electron trajectories 
      using Kalman filters and electron energy clustering based on Geant4 simulation 
      of detector response from LHC physics events.}
  \end{cvitems}
}

%-------------------------------------------------------------------------------
\end{cventries}